---
title: "BMA_try"
author: "Fuyu Guo"
date: '2022-11-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(devtools)
library(BAS)
```

# clean data
```{r}
# use the training dataset
dta <-read_rds("clean_data_whole.rds")
dta <- dta %>% dplyr::select( -c(FAMSIZE, BIRTHYR, YRMARR, DIVINYR,WIDINYR, dataset, DEPARTS, ARRIVES, CLASSWKR, INCBUS00, INCWELFR))

```


- SE:sex
- AGE: age
- MARST: marital status (categorical)
- RACE: ethinicty (categorical)
- HISPAN: Hispanic or not
- HCOVANY: covered by any health insurance, yes or no
- EDUC: Educational experience (categorical)
- UHRS: work hours per week
- WORKEDYR: worked in the last year or not
- INCTOT: Personal total income
- FTOTINC: Family total income
- INCWAGE: Wage and salary income
- VETSTAT: Veteran status, yes or no
- GCHOUSE: have a grandchild in the house
- WORK_STATUS: working status in the last year 

# try BMA with g_prior (sqrt(n))
```{r}
library(tictoc)
tic()
fit1 <- bas.glm(DIFFHEAR~.,
                 family = binomial(),
                 data = dta,
                 betaprior = g.prior(sqrt(dim(dta)[1])),
                 modelprior = beta.binomial(1, 1),
                 method = "MCMC")
toc()
coef(fit1)
saveRDS(fit1, file = "BMA_g_sqrt_N.rds")
```


```{r}
fit <- read_rds("BMA_g_sqrt_N.rds")
summary(fit)
```

```{r}
summary(fit1)
```
```{r}
png("pip_g_sqrt_N.png",
    width = 480, 
    height = 480,
    units = "px")
diagnostics(fit1, type = "pip")
dev.off()


png("post_model_g_sqrt_N.png",
    width = 480, 
    height = 480,
    units = "px")
diagnostics(fit1, type = "model")
dev.off()
```
